Realistically Interesting Domains for Probabilistic Planners

### 2014-04-10 FinalPaper/paper.tex
Use a different wording to start the related work with

%In sections above we have described the GOURMAND planner and FF-Replan as two
%probabilistic planners of the IPPC competition.
%RFF~\cite{teichteil2010incremental} is an offline planner that generates a
%policy: for each reachable state it determines a plan to the goal. Like
%FF-Replan it uses determinization and FF\. FF returns an initial plan from the
%initial state to a goal state. For each state in the plan the successor states
%are added to the structure, after which Monte-Carlo sampling is used. States
%where the probability that they're reached is too low (below a threshold) are
%removed. The successor states are used as initial states in the next step. If
%FF fails to find a plan to the goal from this new state, the state is removed
%from the structure too. Results showed that RFF outperformed other competitors.
%A higher threshold means that RFF will generate more policies that are prone to
%replanning.

\subsubsection{PROST ?}
\todo{wrote sentence about Prost - Arian}\\

@@

To conclude which planner would perform best on the UAV domain, experiments
needs to be executed. The domain can be described in PPDDL
\cite{younes2004ppddl1} or RDDL \cite{Sanner:RDDL}, which are domain
description languages. RDDL is already used by \textsc{Gourmand} while
FF-Replan uses PPDDL\@. FF-Replan could be re-implemented in the
\textsc{Gourmand} framework, using the FF heuristic found in mGPT
\cite{bonet2011planning}. Another possibility is to implement the domain in
both languages and carefully assess if both implementations are fair.  The two
metrics that need to be measured are the rate the goal is reached (and does not
reach dead ends) and the online execution time.

>>>>

FF-Replan replans online, an off-line planner like FF-Replan is RFF
\cite{teichteil2010incremental}. RFF generates policies by determinizing the
given MDP problem, builds partial policies off-line by producing partial
solution plans to the classical planning problem and incrementally aggregating
them into a policy, and using sequential Monte-Carlo simulations to asses the
probability of replanning. Experiments showed that RFF solved more problems
than FF-Replan because it takes the probability a policy has to replan into
account.

PROST \cite{keller2012prost} is a probabilistic planner, which contrary to
\textsc{Gourmand}, is UTC based. It uses techniques to reduce the branching
factor  and limits the search depth so it can focus more on parts that
influence the quality of the resulting policy. Reward lock detection is a
method to detect goals and dead ends in the finite horizon MDP\@. Q-value
Initialization improves the initial start of the UTC algorithm. In the executed
IPPC-11 benchmarks it outperforms other planners such as \textsc{Glutton}.
Later it has been surpassed by \textsc{Gourmand}.

@@
